Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-28 paper.tex
Updates in introduction

\begin{abstract}
  We investigate software architectures commonly used to integrate
  workflow engines in science gateways. We abstract software
  components and interactions in 6 architectures that we use to
  classify 18 systems. We compare these architectures using metrics
  measuring integration challenge, robustness, extensibility, scalability
  and other specific features. Results show the pros and cons of the
  different architectures: tight integration and task encapsulation are the
  simplest architectures and should therefore be the easiest to
  implement and the most robust ones, most architectures perform the
  same in terms of extensibility, the pool model is the most scalable
  and meta-workflows are only available in nested workflows and
  workflow import. Our analysis provides insights for software
  architects on how to integrate science gateways and workflow
  engines.
\end{abstract}

@@

Our analysis is fed by experience gathered from the development and
sustained operation of the CBRAIN~\cite{SHER-14} and
VIP~\cite{GLAT-13} science gateways for medical image analysis during
the past 7 years. It also builds on the lessons learned from several
science gateway and workflow-related projects, including
SHIWA\footnote{\url{http://www.shiwa-workflow.eu}} and related
initiatives.

The remainder of this Section provides background information and
definitions about workflow engines, science gateways and
infrastructures. In Section~\ref{sec:architectures}, we describe 6
architectures in a consistent framework based on the functional
interactions between the main software components involved. In
Section~\ref{sec:evaluation}, we introduce metrics to measure
integration challenge, robustness, extensibility, scalability and other
specific features of the architectures. We use these metrics to
evaluate and compare the 6 architectures. The paper closes on a
discussion and conclusion that highlight architectural recommendations
for science gateway and workflow engine architects.

>>>>

\begin{abstract}
  We investigate software architectures commonly used to integrate
  workflow engines in science gateways. We describe and evaluate 6
  architectures with metrics measuring integration challenge,
  robustness, extensibility, scalability and other specific
  features. Results show the pros and cons of the different
  architectures: tight integration and task encapsulation are the
  simplest architectures and are therefore the easiest to integrate
  and the most robust ones, most architectures perform the same in
  terms of extensibility, the pool model is the most scalable and
  meta-workflows are only available in nested workflows and workflow
  import. Our analysis provides insights for software architects on
  how to integrate science gateways and workflow engines.
\end{abstract}

@@

Our analysis is fed by experience gathered from the development and
sustained operation of the CBRAIN~\cite{SHER-14} and
VIP~\cite{GLAT-13} science gateways for medical image analysis during
the past 7 years. It also builds on the lessons learned from several
science gateway and workflow projects, including
SHIWA\footnote{\url{http://www.shiwa-workflow.eu}} and related
initiatives.

The remainder of this Section provides background information and
definitions about workflow engines, science gateways and
infrastructures. In Section~\ref{sec:architectures}, we describe 6
architectures in a consistent framework that highlight the functional
interactions between their main software components. In
Section~\ref{sec:evaluation}, we evaluate the architectures with
metrics measuring integration challenge, robustness, extensibility,
scalability and other specific features. The paper closes on a
discussion and conclusion that compare architectures and highlight
recommendations for science gateway architects.
